---
title: "Allometry Results"
author: "Zack Brym"
output: html_document
---
##Data
Presented are two blocks of allometry data from my orchard scaling project (2012-2013) conducted at Kaysville Research Farm, USU. I sampled five 24 year old tart cherry (*Prunus cerasus* Montmorency, *P. mahaleb*) from one block and 
19 8 year-old apples (*Malus domestica* "Golden Delicious") from one block with various rootstocks.
BranchSegments.csv (*branch_size*) contains the size and orientation data for all trees sampled at a branch-level.
TreeSummary.csv (*tree_sum*) contains the size and orientation data for all trees sampled at a tree-level. Listing of fields represented in the data are located at the end of this dococument for both data files.
Data is analysed using Standardized Major Axis (SMA; aka reduced major axis) with R-package 'smatr'.  

```{r data_setup, include=FALSE}
branch_size <- read.csv("BranchSegments.csv", sep = ',', header = T)
treesum <- read.csv("TreeSummary.csv", sep = ",", head=T)
apple <- branch_size[branch_size$species == "apple",]
cherry <- branch_size[branch_size$species == "cherry",]
PiAu <- subset(apple, tree==20 | tree==19 | tree==14)
B9 <- subset(apple, tree==2 | tree==7 | tree==12 | tree ==3)
library('smatr')
```

```{r graph_generation_functions, include=FALSE}
tree_graph <- function(x, y, test, pred_b, pred_m, labx, laby, position, R2){
  plot(log10(x[1:19]), log10(y[1:19]), 
       xlim = c((log10(min(x))-0.2),(log10(max(x))+0.2)), ylim = c((log10(min(y))-0.2),(log10(max(y))+0.2)),
       xlab = labx, ylab = laby, cex.lab = 1.5, cex = 2.5, pch = 19, col = "black")
  points(log10(x[20:24]), log10(y[20:24]), cex = 2.5, pch = 19, col = "red", bg = "red")
  abline(sma(test)$coef[[1]][1,1], sma(test)$coef[[1]][2,1], lwd = 3, lty = 2)
  abline(sma(test)$coef[[1]][1,2], sma(test)$coef[[1]][2,2], lwd = 3, lty = 3)
  abline(sma(test)$coef[[1]][1,3], sma(test)$coef[[1]][2,3], lwd = 3, lty = 3)
  abline(pred_b, pred_m, lwd = 3, lty = 1)
  legend(position, legend=R2, bty='n', cex=3)  
} #tree-level figures
branch_graph <- function(x, y, test, pred_b, pred_m, labx, laby, position, R2){
  group_data_x <- list()
  group_data_x[[1]] <- x[x$species=="cherry",]

  apple <- x[x$species=="apple",]
  group_data_x[[2]] <- subset(apple, tree==20 | tree==19 | tree==14)
  group_data_x[[3]] <- subset(apple, tree==17 | tree==15 | tree==18)
  group_data_x[[4]] <- subset(apple, tree==13)
  group_data_x[[5]] <- subset(apple, tree==10 | tree==1 | tree==4 | tree ==9)
  group_data_x[[6]] <- subset(apple, tree==5 | tree==11 | tree==6 | tree ==8)
  group_data_x[[7]] <- subset(apple, tree==2 | tree==7 | tree==12 | tree ==3)
  
  group_data_y <- list()
  group_data_y[[1]] <- y[y$species=="cherry",]
  
  apple <- y[y$species=="apple",]
  group_data_y[[2]] <- subset(apple, tree==20 | tree==19 | tree==14)
  group_data_y[[3]] <- subset(apple, tree==17 | tree==15 | tree==18)
  group_data_y[[4]] <- subset(apple, tree==13)
  group_data_y[[5]] <- subset(apple, tree==10 | tree==1 | tree==4 | tree ==9)
  group_data_y[[6]] <- subset(apple, tree==5 | tree==11 | tree==6 | tree ==8)
  group_data_y[[7]] <- subset(apple, tree==2 | tree==7 | tree==12 | tree ==3)
  
  plot(log10(group_data_x[[1]][,3]), log10(group_data_y[[1]][,3]), 
       xlim = c((log10(min(x[,3], na.rm=T))-0.2),(log10(max(x[,3], na.rm=T))+0.2)), 
       ylim = c((log10(min(y[,3], na.rm=T))-0.2),(log10(max(y[,3], na.rm=T))+0.2)),
       xlab = labx, ylab = laby, cex.lab = 1.5, cex = 1.5, pch = 21, col = "red", bg = "red")
  points(log10(group_data_x[[2]][,3]), log10(group_data_y[[2]][,3]), cex = 1.5, pch = 21, col = "black", bg = "orange")
  points(log10(group_data_x[[3]][,3]), log10(group_data_y[[3]][,3]), cex = 1.5, pch = 21, col = "black", bg = 'yellow')
  points(log10(group_data_x[[4]][,3]), log10(group_data_y[[4]][,3]), cex = 1.5, pch = 21, col = "black", bg = 'green')
  points(log10(group_data_x[[5]][,3]), log10(group_data_y[[5]][,3]), cex = 1.5, pch = 21, col = "black", bg = 'cyan')
  points(log10(group_data_x[[6]][,3]), log10(group_data_y[[6]][,3]), cex = 1.5, pch = 21, col = "black", bg = 'blue')
  points(log10(group_data_x[[7]][,3]), log10(group_data_y[[7]][,3]), cex = 1.5, pch = 21, col = "black", bg = 'purple')
  abline(sma(test)$coef[[1]][1,1], sma(test)$coef[[1]][2,1], lwd = 3, lty = 2)
  abline(sma(test)$coef[[1]][1,2], sma(test)$coef[[1]][2,2], lwd = 3, lty = 3)
  abline(sma(test)$coef[[1]][1,3], sma(test)$coef[[1]][2,3], lwd = 3, lty = 3)
  abline(pred_b, pred_m, lwd = 3, lty = 1)
  legend(position, legend=R2, bty='n', cex=3)  
} #branch-level log10-trans
branch_graph2 <- function(x, y, test, pred_b, pred_m, labx, laby, position, R2){
  group_data_x <- list()
  group_data_x[[1]] <- x[x$species=="cherry",]
  
  apple <- x[x$species=="apple",]
  group_data_x[[2]] <- subset(apple, tree==20 | tree==19 | tree==14)
  group_data_x[[3]] <- subset(apple, tree==17 | tree==15 | tree==18)
  group_data_x[[4]] <- subset(apple, tree==13)
  group_data_x[[5]] <- subset(apple, tree==10 | tree==1 | tree==4 | tree ==9)
  group_data_x[[6]] <- subset(apple, tree==5 | tree==11 | tree==6 | tree ==8)
  group_data_x[[7]] <- subset(apple, tree==2 | tree==7 | tree==12 | tree ==3)
  
  group_data_y <- list()
  group_data_y[[1]] <- y[y$species=="cherry",]
  
  apple <- y[y$species=="apple",]
  group_data_y[[2]] <- subset(apple, tree==20 | tree==19 | tree==14)
  group_data_y[[3]] <- subset(apple, tree==17 | tree==15 | tree==18)
  group_data_y[[4]] <- subset(apple, tree==13)
  group_data_y[[5]] <- subset(apple, tree==10 | tree==1 | tree==4 | tree ==9)
  group_data_y[[6]] <- subset(apple, tree==5 | tree==11 | tree==6 | tree ==8)
  group_data_y[[7]] <- subset(apple, tree==2 | tree==7 | tree==12 | tree ==3)
  
  plot(group_data_x[[1]][,3], group_data_y[[1]][,3], 
       xlim = c((min(x[,3], na.rm=T)-0.2),(max(x[,3], na.rm=T)+0.2)), 
       ylim = c((min(y[,3], na.rm=T)-0.2),(max(y[,3], na.rm=T)+0.2)),
       xlab = labx, ylab = laby, cex.lab = 1.5, cex = 1.5, pch = 21, col = "red", bg = "red")
  points(group_data_x[[2]][,3], group_data_y[[2]][,3], cex = 1.5, pch = 21, col = "black", bg = "orange")
  points(group_data_x[[3]][,3], group_data_y[[3]][,3], cex = 1.5, pch = 21, col = "black", bg = 'yellow')
  points(group_data_x[[4]][,3], group_data_y[[4]][,3], cex = 1.5, pch = 21, col = "black", bg = 'green')
  points(group_data_x[[5]][,3], group_data_y[[5]][,3], cex = 1.5, pch = 21, col = "black", bg = 'cyan')
  points(group_data_x[[6]][,3], group_data_y[[6]][,3], cex = 1.5, pch = 21, col = "black", bg = 'blue')
  points(group_data_x[[7]][,3], group_data_y[[7]][,3], cex = 1.5, pch = 21, col = "black", bg = 'purple')
  abline(sma(test)$coef[[1]][1,1], sma(test)$coef[[1]][2,1], lwd = 3, lty = 2)
  abline(sma(test)$coef[[1]][1,2], sma(test)$coef[[1]][2,2], lwd = 3, lty = 3)
  abline(sma(test)$coef[[1]][1,3], sma(test)$coef[[1]][2,3], lwd = 3, lty = 3)
  abline(pred_b, pred_m, lwd = 3, lty = 1)
  legend(position, legend=R2, bty='n', cex=3)  
} #branch-level no log-trans
```

##Frequency Distributions

###Length Histograms
Histograms for segment length [cm], path length, and subtree length levels. Sample size is listed next to title. There are 5 cherry and 19 apple individuals represented. The Biggest Apple is the largest rootstock ('PiAu') with 3 individuals represented. The Smallest Apple is the smallest rootstock ('B9') with 4 individuals represented.  
  
* *I'd like to use this data to determine if the tree is fractal (Log-Log or Log-Linear), but my notes are unclear how exactly to do that. Please, help.* *

####Segment Length
Segment length is the distance of a branch unit bounded by two major branching events.
```{r length_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$length_cm, main = paste("All ( n =",length(branch_size$length_cm),")"), breaks = 40, xlab="Segment Length")
hist(cherry$length_cm, main = paste("Cherry ( n =",length(cherry$length_cm),")"), breaks = 40, xlab = "Segment Length")
hist(apple$length_cm, main = paste("Apple ( n =",length(apple$length_cm),")"), breaks = 40, xlab = "Segment Length")
hist(PiAu$length_cm, main = paste("Biggest Apples ( n =",length(PiAu$length_cm),")"),breaks = 20,xlab = "Segment Length")
hist(B9$length_cm, main = paste("Smallest Apples ( n =",length(B9$length_cm),")"), breaks = 20, xlab = "Segment Length")
```

####Path Length
Path length is the total length of a target branch and the longest continuous length of succeding branches. The calculation includes terminal twigs when the data is available.
```{r pathlength_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$path_length, main = paste("All ( n =",length(branch_size$length_cm),")"), breaks = 40, xlab="Path Length")
hist(cherry$path_length, main = paste("Cherry ( n =",length(cherry$length_cm),")"), breaks = 40, xlab = "Path Length")
hist(apple$path_length, main = paste("Apple ( n =",length(apple$length_cm),")"), breaks = 40, xlab = "Path Length")
hist(PiAu$path_length, main = paste("Biggest Apples ( n =",length(PiAu$length_cm),")"), breaks = 20, xlab="Path Length")
hist(B9$path_length, main = paste("Smallest Apples ( n =",length(B9$length_cm),")"), breaks = 20, xlab = "Path Length")
```

####Subtree Length *(includes terminal twigs when possible)*
Subtree is the diameter of a given branch segment, and the total length, total surface area, and total volume of all branch segments distal to that branch segment.

```{r subtreelength_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$tot_length, main = paste("All ( n =",length(branch_size$tot_length),")"), breaks=60, xlab="Sum of Lengths")
hist(cherry$tot_length, main = paste("Cherry ( n =",length(cherry$tot_length),")"), breaks = 60, xlab = "Sum of Lengths")
hist(apple$tot_length, main = paste("Apple ( n =",length(apple$tot_length),")"), breaks = 60, xlab = "Sum of Lengths")
hist(PiAu$tot_length, main = paste("Biggest Apples ( n =",length(PiAu$tot_length),")"), breaks = 60, xlab="Sum of Lengths")
hist(B9$tot_length, main = paste("Smallest Apples ( n =",length(B9$tot_length),")"), breaks = 60, xlab = "Sum of Lengths")
```

###Diameter Histograms
Histograms for diameter [mm] at an individual level. Sample size is listed next to title. There are 5 cherry and 19 apple individuals represented. The Biggest Apple is the largest rootstock ('PiAu') with 3 individuals represented. The Smallest Apple is the smallest rootstock ('B9') with 4 individuals represented.   
```{r diameter_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$diameter_mm, main = paste("All ( n =",length(branch_size[,1]),")"), breaks = 40, xlab="Diameter")
hist(cherry$diameter_mm, main = paste("Cherry ( n =",length(cherry[,1]),")"), breaks = 40, xlab = "Diameter")
hist(apple$diameter_mm, main = paste("Apple ( n =",length(apple[,1]),")"), breaks = 40, xlab = "Diameter")
hist(PiAu$diameter_mm, main = paste("Biggest Apples ( n =",length(PiAu[,1]),")"),breaks = 20,xlab = "Diameter")
hist(B9$diameter_mm, main = paste("Smallest Apples ( n =",length(B9[,1]),")"), breaks = 20, xlab = "Diameter")
```

###Mass Histograms
Histograms for segment mass, total segment mass, and total subtree mass. Sample size is listed next to title. There are 5 cherry and 19 apple individuals represented. The Biggest Apple is the largest rootstock ('PiAu') with 3 individuals represented. The Smallest Apple is the smallest rootstock ('B9') with 4 individuals represented.  

####Segment Mass
```{r mass_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$stem_m, main = paste("All ( n =",length(branch_size[,1]),")"), breaks = 40, xlab="Segment Mass")
hist(cherry$stem_m, main = paste("Cherry ( n =",length(cherry[,1]),")"), breaks = 40, xlab = "Segment Mass")
hist(apple$stem_m, main = paste("Apple ( n =",length(apple[,1]),")"), breaks = 40, xlab = "Segment Mass")
hist(PiAu$stem_m, main = paste("Biggest Apples ( n =",length(PiAu[,1]),")"),breaks = 20,xlab = "Segment Mass")
hist(B9$stem_m, main = paste("Smallest Apples ( n =",length(B9[,1]),")"), breaks = 20, xlab = "Segment Mass")
```

####Total Segment Mass 
Total Segment Mass is the the sum of all major branch segments. Terminal twigs are not included.
```{r totmass_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$tot_stem_m, main = paste("All ( n =",length(branch_size[,1]),")"), breaks = 40, xlab="Total Segment Mass")
hist(cherry$tot_stem_m, main = paste("Cherry ( n =",length(cherry[,1]),")"), breaks = 40, xlab = "Total Segment Mass")
hist(apple$tot_stem_m, main = paste("Apple ( n =",length(apple[,1]),")"), breaks = 40, xlab = "Total Segment Mass")
hist(PiAu$tot_stem_m, main = paste("Biggest Apples ( n =",length(PiAu[,1]),")"),breaks = 20,xlab = "Total Segment Mass")
hist(B9$tot_stem_m, main = paste("Smallest Apples ( n =",length(B9[,1]),")"), breaks = 20, xlab = "Total Segment Mass")
```

####Subtree Mass 
Subtree mass is the total sum of all major branch and twig segments. Twig mass is added to Total Segment Mass.
```{r subtreemass_hist, echo=FALSE}
par(mfrow = c(2,3))
hist((branch_size$tot_stem_m + branch_size$tot_twig_m), 
     main = paste("All ( n =",length(branch_size[,1]),")"), breaks = 40, xlab="Total Subtree Mass")
hist((cherry$tot_stem_m + cherry$tot_twig_m), 
     main = paste("Cherry ( n =",length(cherry[,1]),")"), breaks = 40, xlab = "Total Subtree Mass")
hist((apple$tot_stem_m + apple$tot_twig_m), 
     main = paste("Apple ( n =",length(apple[,1]),")"), breaks = 40, xlab = "Total Subtree Mass")
hist((PiAu$tot_stem_m + PiAu$tot_twig_m), 
     main = paste("Biggest Apples ( n =",length(PiAu[,1]),")"),breaks = 20,xlab = "Total Subtree Mass")
hist((B9$tot_stem_m + B9$tot_twig_m), 
     main = paste("Smallest Apples ( n =",length(B9[,1]),")"), breaks = 20, xlab = "Total Subtree Mass")
```

###Daughter/Parent Branch Area Ratio Histograms
The Branch Area Ratio is sum of daughter branch surface areas divided by the surface area of their parent branch.
```{r arearatio_hist, echo=FALSE}
par(mfrow = c(2,3))
hist(branch_size$area_ratio, main = paste("All ( Mean =", round(mean(branch_size$area_ratio, na.rm = TRUE),3),")"), 
     breaks = 40, xlab="Branch Area Ratio")
abline(v=mean(branch_size$area_ratio, na.rm = TRUE), lwd = 3, lty = 1)
hist(cherry$area_ratio, main = paste("Cherry ( Mean =", round(mean(cherry$area_ratio, na.rm = TRUE),3),")"), breaks = 40, 
     xlab = "Branch Area Ratio")
abline(v=mean(cherry$area_ratio, na.rm = TRUE), lwd = 3, lty = 1)
hist(apple$area_ratio, main = paste("Apple ( Mean =", round(mean(apple$area_ratio, na.rm = TRUE),3),")"), breaks = 40, 
     xlab = "Branch Area Ratio")
abline(v=mean(apple$area_ratio, na.rm = TRUE), lwd = 3, lty = 1)
hist(PiAu$area_ratio, main = paste("Biggest Apples ( Mean =", round(mean(PiAu$area_ratio, na.rm = TRUE),3),")"),breaks = 20,
     xlab = "Branch Area Ratio")
abline(v=mean(PiAu$area_ratio, na.rm = TRUE), lwd = 3, lty = 1)
hist(B9$area_ratio, main = paste("Smallest Apples ( Mean =", round(mean(B9$area_ratio, na.rm = TRUE),3),")"), breaks = 20, 
     xlab = "Branch Area Ratio")
abline(v=mean(B9$area_ratio, na.rm = TRUE), lwd = 3, lty = 1)
```

##Scaling Relationships 

###Length  ~ Diameter
Expected Exponent: Flow Similarity = 2 (peripheral / fruiting branches); Biomechanical = 2/3 (basal / scaffold branches)

#### Tree Height [Estimated: 0.74 +/- 0.12, R2 = 0.849] 
```{r Diameter_Height_output, echo=FALSE}
par(mfrow = c(1,1))
Diameter_Height <- sma(log10(treesum$height)~log10(treesum$trunk_diam))
tree_graph(treesum$trunk_diam, treesum$height, Diameter_Height, 0, 0,
           "log ( Trunk Diameter  )", "log ( Height )", 'bottomright', expression(R^2 == 0.849))
```

####Segment Length [Estimated: 0.90 +/- 0.06, R2 = 0.005]
```{r diameter_length_output, echo=FALSE}
length_zeros = branch_size[branch_size$length_cm > 0,]
diameter_length <- sma(log10(length_zeros$length_cm)~log10(length_zeros$diameter_mm))
branch_graph(subset(length_zeros, select = c(species, tree, diameter_mm)),
             subset(length_zeros, select = c(species, tree, length_cm)),
             diameter_length, 0, 0, "log ( Diameter  )", "log ( Segment Length )",
             'bottomright', expression(R^2 == 0.005))
```

####Path Length [Estimated: 0.86 +/- 0.04, R2 = 0.448]
```{r diameter_path_output, echo=FALSE}
diameter_path <- sma(log10(branch_size$path_length)~log10(branch_size$diameter_mm))
branch_graph(subset(branch_size, select = c(species, tree, diameter_mm)),
             subset(branch_size, select = c(species, tree, path_length)),
             diameter_path, 0, 0, "log ( Diameter  )", "log ( Path Length )",
             'bottomright', expression(R^2 == 0.442))
```

####Total Subtree Length [Estimated: 1.72 +/- 0.10, R2 = 0.230]
```{r diameter_totlength_output, echo=FALSE}
diameter_totlength <- sma(log10(branch_size$tot_length)~log10(branch_size$diameter_mm))
branch_graph(subset(branch_size, select = c(species, tree, diameter_mm)),
             subset(branch_size, select = c(species, tree, tot_length)),
             diameter_totlength, 0, 0,"log ( Diameter  )","log ( Subtree Length )" ,
             'bottomright', expression(R^2 == 0.230))
```

###Surface Area ~ Volume 
Expected Exponent: Flow Similarity = 3/4 ; Biomechanical = 5/8

####Segment Level [Estimated: 0.62 +/- 0.01, R2 = 0.918]
```{r area_volume_output, echo=FALSE}
area_volume <- sma(log10(branch_size$area)~log10(branch_size$volume))
branch_graph(subset(branch_size, select = c(species, tree, volume)),
             subset(branch_size, select = c(species, tree, area)),
             area_volume, 0, 0,"log ( Segment Volume  )","log ( Segment Surface Area )" ,
             'bottomright', expression(R^2 == 0.918))
```

####Subtree Level [Estimated: 0.72 +/- 0.01, R2 = 0.969]
```{r totarea_totvolume_output, echo=FALSE}
totarea_totvolume <- sma(log10(branch_size$tot_area)~log10(branch_size$tot_volume))
branch_graph(subset(branch_size, select = c(species, tree, tot_volume)),
             subset(branch_size, select = c(species, tree, tot_area)),
             totarea_totvolume, 0, 0,"log ( Subtree Volume  )","log ( Subtree Surface Area )" ,
             'bottomright', expression(R^2 == 0.969))
```

### Diameter ~ Volume
Expected Exponent: Flow Similarity = 1/4 ; Biomechanical = 3/8

####Segment Level [Estimated: 0.44 +/- 0.01, R2 = 0.841]
```{r diameter_volume_output, echo=FALSE}
diameter_volume <- sma(log10(branch_size$diameter_mm)~log10(branch_size$volume))
branch_graph(subset(branch_size, select = c(species, tree, volume)),
             subset(branch_size, select = c(species, tree, diameter_mm)),
             diameter_volume, -1, 0,"log ( Segment Volume  )","log ( Diameter )" ,
             'bottomright', expression(R^2 == 0.841))
```

####Subtree Level [Estimated: 0.38 +/- 0.01, R2 = 0.938]
```{r diameter_totvolume_output, echo=FALSE}
diameter_totvolume <- sma(log10(branch_size$diameter_mm)~log10(branch_size$tot_volume))
branch_graph(subset(branch_size, select = c(species, tree, tot_volume)),
             subset(branch_size, select = c(species, tree, diameter_mm)),
             diameter_totvolume, -1, 0,"log ( Subtree Volume  )","log ( Diameter )" ,
             'bottomright', expression(R^2 == 0.938))
```

### Length ~ Volume
Expected Exponent: Flow Similarity = 1/2 ; Biomechanical = 1/4

####Segment Level [Estimated: 0.39 +/- 0.03, R2 = 0.219]
```{r volume_length_output, echo=FALSE}
length_zeros = branch_size[branch_size$length_cm > 0,]
volume_length <- sma(log10(length_zeros$length_cm)~log10(length_zeros$volume))
branch_graph(subset(length_zeros, select = c(species, tree, volume)),
             subset(length_zeros, select = c(species, tree, length_cm)),
             volume_length, 0, 0, "log ( Segment Volume  )", "log ( Segment Length )",
             'bottomright', expression(R^2 == 0.219))
```

####Subtree Level [Estimated: 0.67 +/- 0.04, R2 = 0.294]
```{r totvolume_totlength_output, echo=FALSE}
totvolume_totlength <- sma(log10(branch_size$tot_length)~log10(branch_size$tot_volume))
branch_graph(subset(branch_size, select = c(species, tree, tot_volume)),
             subset(branch_size, select = c(species, tree, tot_length)),
             totvolume_totlength, 0, 0,"log ( Subtree Volume  )","log ( Subtree Length )" ,
             'bottomright', expression(R^2 == 0.294))
```

### Diameter ~ Surface Area
Expected Exponent: Flow Similarity = 1/3 ; Biomechanical = 3/5

####Segment Level [Estimated: 0.71 +/- 0.03, R2 = 0.586]
```{r diameter_area_output, echo=FALSE}
diameter_area <- sma(log10(branch_size$diameter_mm)~log10(branch_size$area))
branch_graph(subset(branch_size, select = c(species, tree, area)),
             subset(branch_size, select = c(species, tree, diameter_mm)),
             diameter_area, -1, 0,"log ( Segment Surface Area  )","log ( Diameter )" ,
             'bottomright', expression(R^2 == 0.586))
```

####Subtree Level [Estimated: 0.53 +/- 0.01, R2 = 0.859]
```{r diameter_totarea_output, echo=FALSE}
diameter_totarea <- sma(log10(branch_size$diameter_mm)~log10(branch_size$tot_area))
branch_graph(subset(branch_size, select = c(species, tree, tot_area)),
             subset(branch_size, select = c(species, tree, diameter_mm)),
             diameter_totarea, -1, 0,"log ( Subtree Surface Area  )","log ( Diameter )" ,
             'bottomright', expression(R^2 == 0.859))
```

### Length ~ Surface Area
Expected Exponent: Flow Similarity = 2/3 ; Biomechanical = 2/5

####Segment Level [Estimated: 0.64 +/- 0.03, R2 = 0.491]
```{r area_length_output, echo=FALSE}
area_length <- sma(log10(length_zeros$length_cm)~log10(length_zeros$area))
branch_graph(subset(length_zeros, select = c(species, tree, area)),
             subset(length_zeros, select = c(species, tree, length_cm)),
             area_length, 0, 0, "log ( Segment Surface Area  )", "log ( Segment Length )",
             'bottomright', expression(R^2 == 0.491))
```

####Subtree Level [Estimated: 0.93 +/- 0.05, R2 = 0.391]
```{r totarea_totlength_output, echo=FALSE}
totarea_totlength <- sma(log10(branch_size$tot_length)~log10(branch_size$tot_area))
branch_graph(subset(branch_size, select = c(species, tree, tot_area)),
             subset(branch_size, select = c(species, tree, tot_length)),
             totarea_totlength, 0, 0,"log ( Subtree Surface Area  )","log ( Subtree Length )" ,
             'bottomright', expression(R^2 == 0.391))
```

### Length ~ Mass

#### Tree Level [Estimated: 0.30 +/- 0.05, R2 = 0.849]
```{r Height_Mass_output, echo=FALSE}
Height_Mass <- sma(log10(treesum$height)~log10(treesum$tot_stem_m))
tree_graph(treesum$tot_stem_m, treesum$height, Height_Mass, sma(Height_Mass)$coef[[1]][2,1], 0.25,
           "log ( Total Stem Mass  )", "log ( Height )", 'bottomright', expression(R^2 == 0.849))
```
  

#### Branch Level [Estimated: 0.35 +/- 0.1, R2 = 0.632]
```{r length_mass_output, echo=FALSE}
length_mass <- sma(log10(branch_size$path_length)~log10(branch_size$tot_stem_m))
branch_graph(subset(branch_size, select = c(species, tree, tot_stem_m)),
             subset(branch_size, select = c(species, tree, path_length)),
             length_mass, 0, 0, "log ( Total Stem Mass  )", "log ( Path Length )",
             'bottomright', expression(R^2 == 0.632))
```
  

### Mass ~ Diameter
  
#### Tree Level [Estimated: 2.49 +/- 0.18, R2 = 0.974]
```{r Diameter_Mass_output, echo=FALSE}
Diameter_Mass <- sma(log10(treesum$tot_stem_m)~log10(treesum$trunk_diam), slope.test = 2.67)
tree_graph(treesum$trunk_diam, treesum$tot_stem_m, Diameter_Mass, 0, 2.67,
           "log ( Trunk Diameter  )", "log ( Total Stem Mass )", 'bottomright', expression(R^2 == 0.974))
```  
  
  
#### Branch Level [Estimated 2.48 +/- 0.05, R2 = 0.905]
```{r diameter_mass_output, echo=FALSE}
diameter_mass <- sma(log10(branch_size$tot_stem_m)~log10(branch_size$diameter_mm))
branch_graph(subset(branch_size, select = c(species, tree, diameter_mm)),
             subset(branch_size, select = c(species, tree, tot_stem_m)),
             diameter_mass, 0, 2.67, "log ( Diameter  )", "log ( Total Stem Mass )",
             'bottomright', expression(R^2 == 0.905))
```
 
### Mass ~ Volume (Wood Density) 

#### Segment Level [Estimated: 0.95 +/- 0.01, R2 = 0.962]
```{r mass_volume_output, echo=FALSE}
mass_zero <- branch_size[branch_size$stem_m > 0,]
mass_volume <- sma(log10(mass_zero$stem_m)~log10(mass_zero$volume))
branch_graph(subset(mass_zero, select = c(species, tree, volume)),
             subset(mass_zero, select = c(species, tree, stem_m)),
             mass_volume, -1, 0,"log ( Segment Volume  )","log ( Segment Mass )" ,
             'bottomright', expression(R^2 == 0.962))
```

####Subtree Level [Estimated: 0.95 +/- 0.01, R2 = 0.977]
```{r totmass_totvolume_output, echo=FALSE}
totmass_totvolume <- sma(log10(branch_size$tot_stem_m)~log10(branch_size$tot_volume))
branch_graph(subset(branch_size, select = c(species, tree, tot_volume)),
             subset(branch_size, select = c(species, tree, tot_stem_m)),
             totmass_totvolume, -1, 0,"log ( Subtree Volume  )","log ( Subtree Mass )" ,
             'bottomright', expression(R^2 == 0.977))
```

   
### Diameter ~ No of terminal branches

####[Estimated: 0.69 +/- 0.03, R2 = 0.429
```{r diameter_tottwigs_output, echo=FALSE}
twigs_zero <- branch_size[branch_size$tot_no_twigs > 0,]
diameter_tottwigs <- sma(log10(twigs_zero$diameter_mm)~log10(twigs_zero$tot_no_twigs))
branch_graph(subset(twigs_zero, select = c(species, tree, tot_no_twigs)),
             subset(twigs_zero, select = c(species, tree, diameter_mm)),
             diameter_tottwigs, -1, 0,"log ( No. of Terminal Points )", "log ( Diameter )",
             'bottomright', expression(R^2 == 0.429))
```

### Surface Area ~ No of terminal branches

####[Estimated: 1.29 +/- 0.05, R2 = 0.669]
```{r totarea_tottwigs_output, echo=FALSE}
twigs_zero <- branch_size[branch_size$tot_no_twigs > 0,]
totarea_tottwigs <- sma(log10(twigs_zero$tot_area)~log10(twigs_zero$tot_no_twigs))
branch_graph(subset(twigs_zero, select = c(species, tree, tot_no_twigs)),
             subset(twigs_zero, select = c(species, tree, tot_area)),
             totarea_tottwigs, 0, 0,"log ( No. of Terminal Points )", "log ( Subtree Area  )",
             'bottomright', expression(R^2 == 0.669))
```


### Diameter Ratio
The Diameter Ratio is a pairwise relationship of a daughter segment to its parent.

####[Estimate: 0.68 +/- 0.03, R2 = 0.569]
```{r diameterratio_output, echo=FALSE}
dratio_temp_na <- subset(branch_size, select = c(species, tree, diameter_mm, diameter_ratio))
dratio_temp <- na.omit(dratio_temp_na)
parent_diam <- data.frame(species = dratio_temp$species, tree = dratio_temp$tree,
                          ratio = dratio_temp$diameter_mm/dratio_temp$diameter_ratio)

diameter_ratio <- sma(dratio_temp$diameter_mm~parent_diam$ratio)
branch_graph2(parent_diam, dratio_temp, diameter_ratio, -10, 0, "Parent Diameter", "Daughter Diameter",
             'topleft', expression(R^2 == 0.632))
```
