---
title: "2002 Goldens Root Biomass Results"
author: "Prepared by: Zack Brym"
date: "May 20, 2015"
output: html_document
---

```{r, include=FALSE}
source('~/Desktop/branch-arch/NC140/root-yield.R', echo = FALSE)
```
#Summary Tables

##Total Mass By Location (i.e., Tree)

```{r, echo=FALSE}
print(tree_totals)
```

##Average Mass By Rootstock
```{r, echo=FALSE}
print(roots_totals)
```

#Duncan's Test Restuls

## by rootstock
I used the summarized data by tree to evaluate a simplified rootstock effect. 
Results are given for stump mass, total mass and each size-class.
The ANOVA model is: `root_mass ~ rootstock`
```{r, echo=FALSE}
masses <- c("STUMP", "TOTAL", "LARGE", "MEDIUM", "SMALL")
for (i in c(1:5)){
  cat(masses[i], "\n")
  print(summary_rootstock[[i]])
  cat("\n")
  print(duncan_rootstock[[i]])
  cat("\n")
}
```

## by location by rootstock
I used the raw data by rootstock, location, and depth to evaluate location and rootstock
effect on root biomass. Results are given for total mass and each size-class.
The ANOVA model is: `root_mass ~ rootstock*locaton`
From what I'm reading about split-factor design and analysis, this model might 
be defined incorrectly to introduce pseudoreplication. I explored defining the
model with error terms, but was unable to pass any of those results to the 
Duncan test. I don't know enough about ANOVA to determine the most appropriate
model formulation and analysis proceedure.

```{r, echo=FALSE}
masses <- c("TOTAL", "LARGE", "MEDIUM", "SMALL")
for (i in c(1:4)){
  cat(masses[i], "\n")
  print(summary_location[[i]])
  cat("\n")
  print(duncan_location[[i]])
  cat("\n")
}
```

## by depth by location by rootstock
I used the raw data by rootstock, location, and depth to evaluate differences in 
mass. Results are given for total mass and each size-class.
The ANOVA model is: `root_mass ~ rootstock*locaton*depth`
We should be able to use this single analysis to interpret all levels of effect.

```{r, echo=FALSE}
masses <- c("TOTAL", "LARGE", "MEDIUM", "SMALL")
for (i in c(1:4)){
  cat(masses[i], "\n")
  print(summary_depth[[i]])
  cat("\n")
  print(duncan_depth[[i]])
  cat("\n")
}
```